### 2009-04-14 docs/survival/survival.tex
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@214 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection{Left censored observations $E_i =2$}
I'm a bit confused about this one...  For completeness we should define the likelihood for left censoring with left truncation.
\begin{align*}
pr(U_i, E_i=2 | C_i) =& pr(C_i < T_i < U_i | T_i > C_i, Y_i =0) pr(Y_i =0) \\
=&pr(C_i < T_i <U_i) pr(Y_i = 0)/pr(T_i > C_i) \\
=& (1-\rho) \left. \int_{C_i}^{U_i} f(x;\gamma_i, \nu) dx \right/\int_{C_i}^\infty f(x;\gamma_i, \nu) dx  \\
= &    (1-\rho) \left. \left[\exp(-\gamma_i C_i^\nu) - \exp(-\gamma_i U_i^\nu) \right] \right/\exp\left[-\gamma_i C_i^\nu\right]\\
= &  (1-\rho)\left\{1 -  \exp\left[\gamma_i\left(C_i^\nu -U_i^\nu\right)\right] \right\} \\
\end{align*}

>>>>

\subsection{Left censored observations $E_i =2$}
For completeness wedefine the likelihood for left censoring with left truncation.
\begin{align*}
pr(U_i, E_i=2 | C_i) =& pr(T_i < U_i | T_i > C_i, Y_i =0) pr(Y_i =0) \\
=&pr(C_i < T_i <U_i) pr(Y_i = 0)/pr(T_i > C_i) \\
=& (1-\rho) \left. \int_{C_i}^{U_i} f(x;\gamma_i, \nu) dx \right/\int_{C_i}^\infty f(x;\gamma_i, \nu) dx  \\
= &    (1-\rho) \left. \left[\exp(-\gamma_i C_i^\nu) - \exp(-\gamma_i U_i^\nu) \right] \right/\exp\left[-\gamma_i C_i^\nu\right]\\
= &  (1-\rho)\left\{1 -  \exp\left[\gamma_i\left(C_i^\nu -U_i^\nu\right)\right] \right\} \\
\end{align*}
